\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{references.bib}
\usepackage{amsmath}  % Basic math symbols and environments
\usepackage{amssymb}  % Extended symbol collection
\usepackage{mathtools} % Fixes and additions to amsmath
\usepackage{algorithm}
\usepackage{algpseudocode}
\begin{document}
\title{AIML427 - Big Data Assignment \#1}
\section{Classification, Regression and Clustering}

These answers will deal with a single dataset, browser analytics events with backing system RPCs. The business has 10m users. ARPU is currently \(USD\ \$160/user/year\) \cite{arpu}. Total revenue is USD \$1.6billion. Each session will generate 100 clicks, and 100 front end RPCs. Each front-end RPC generates 100 back end calls. Users will interact with the system daily. To deal with seasonal variations in data, we need to store and process at least a full year's worth of data. 

Therefore the \textbf{volume} and \textbf{velocity} of data involved is roughly:

\begin{center}
	\begin{tabular}{|c c | c c|}
	\hline
	    \textbf{variable} & \textbf{description} & \textbf{variable} & \textbf{description}\\
	    \(S_d\) & sessions per day = 1 & \(C_s\) & clicks per session = 100\\
	    \(F_s\) & front-end RPCs per session = 100 & \(B_f\) & back-end RPCs per F\_s = 100\\
	    \(E_s\) & events per session & \(B_e\) & bytes per event = 100\\
	    \(B_s\) & bytes per session = 1000 & \(T_b\) & total data size\\
	    \(N_d\) & total number of days stored & \(T_e\) & total events stored analyzed per user\\
	\hline
	\end{tabular}
\end{center}

\begin{align*}
	E_s &= C_s + F_s + F_s * B_f\\
	T_e &= N_d * S_d * E_s\\
	&= N_d * S_d * (C_s + F_s + F_s * B_f)\\
	T_b &= (S_d * N_d * B_s + T_e * B_e) * U\\
	&= 3.73 \text{ petabytes per year}\\
	&= 946Mb/s.
\end{align*}

\section*{big data classification example}

 A model can be trained to predict if a user may be a fraudster, using the user event stream, including a "deemed fraudster" event. The "deemed fraudster" event would be removed from the stream and used as the label for training.

Since the dataset is labelled, this is a \textbf{classification} problem.

If the company cannot keep payment fraud under control, processors will increase merchant fees, or even disconnect the company from payment networks. The fraud loss ratio is currently 1.8\% of revenue \cite{ccfraud}, providing a \textbf{value} of USD \$32.4million.

Both fraudsters and the system will change. The model will need to be retrained frequently. If the model is retrained every month, and the data should be no more than 2 weeks old at launch, the system needs to process \(\frac{3.73PB}{2\ weeks} = 25Gbps\).

\section*{big data regression example}

The dataset includes a "purchase" event, with the cart value. We can label the user with the total spent over the past year. The goal is to predict a customer's total spend from the event stream. Since the dataset is labelled with a continuous value, it is a \textbf{regression} problem.

The ability to better target spending is of significant \textbf{value} to the business. A 1\% improvement in transaction completion is worth USD \$18million

\section*{big data clustering example}

The model should detect significant differences in sessions - too short, too long, or containing strange interactions.

There aren't any labels - this is a \textbf{clustering problem}. Every completed session's event stream will be evaluated against the model to determine if it is an anomaly, where "anomaly" is defined as "being too far away from any of the clusters".

The alerting system would count sessions reported anomalous by the model, and if they exceed a certain rate (or ratio), trigger an alert. The business \textbf{value} is in reducing revenue loss and escalations. Going from 3 9's to 5 9's of downtime would be worth USD \$2million in immediate revenue.

In Anomaly detection, we again want short training intervals, with a lag in the training data window to avoid boiling the frog as bad features are incrementally rolled out. This would still require training every month, requiring \(25Gbps\) of processing.

\section{Feature Selection/Construction Methods}

\subsection{feature ranking/feature weighting vs feature
	subset selection methods}
	
Feature Ranking is a global ordering of features, where each feature is evaluated once. This will then be used by a greedy subset search algorithm which will pick the top-K 
features \cite{week3fsfilter}.

Feature Subset Selection will iterate over subsets and evaluate each subset, selecting the best from those reachable using the algorithm.

Feature Ranking is very quick to perform typically \(O(N)\), but does not consider interactions between features. Feature Subset Selection can take significantly more time, a complete search would require \(2^N\) iterations.

One example is the Pearson Correlation Coefficient \cite{pearson1895note}, which measures the linear relationship between a feature and a class label, using the covariance and standard deviation of each feature and class label.

A second is Information Gain, the feature selector used in ID3 Decision Trees \cite{quinlan:induction}. The information gain for a feature is:

\begin{flalign}
	&& \text{for every value in feature} \\
	&& entropy = -\sum p_i log_2 p_i\\
	&& ig = entropy_{parent} - \sum{size(child)/size(parent) * entropy_{child}}\\
\end{flalign}

Feature Subset Selection is a search algorithm, producing candidate subsets for evaluation. One example is Sequential Forward Search \cite{week2featmanip}. At each stage, the proposed feature set is grown by adding the "best" feature from the remaining set. When the set's quality exceeds a defined threshold, the algorithm completes and returns the current set.

Another search algorithm is Beam Search \cite{harpy}, where, instead of a single set Y growing, there are N sets. At each iteration, the N sets are grown, with the best N results kept. This allows the search to spread out and test hypotheses.

\subsection{Define Filter, Wrapper, Embedded Feature Selection/Construction}

The Filter feature selection/construction method involves a single pass through the features and then sorting to produce the subset. It is the cheapest to execute, produces the most generalizable set but is not tuned for the specific problem.

Primary Component Analysis is a Filter Feature Construction method - \cite{FRS1901LIIIOL}. It takes the data and constructs a set of Eigenvectors. The Eigenvectors are then sorted by the Eigenvalues and the top-K selected. This constructs a new feature set of size K, composed linearly from the existing parameters.

Relief is a Filter Feature Selection method \cite{Kira1992TheFS}. It randomly picks values from the dataset, and uses Euclidean distance to find features that are able to find class boundaries.

On each value, it looks for the closest miss and the closest row with the same label (near hit), and the closest row with a different label (near miss). It then updates the weights of features based on the following equation:

\begin{align}
W_{i}=W_{i} - \mathrm{diff}(x_{i},\mathrm{nearHit})^2 + \mathrm{diff}(x_{i},\mathrm{nearMiss})^2
\end{align}
This will make features that tend to cluster near similar targets unimportant, while features that find edges (near miss) more important.

Wrapper feature selection methods have two phases. There is a subset selection algorithm and then the wrapped machine learning algorithm. The enclosed algorithm is the same as the one which will be used for the final training pass.

Since the enclosed algorithm is problem-specific, the subset search algorithms are the differentiators. Two of these were already discussed under subset selection.

A third subset search algorithm is Sequential Backwards Search \cite{week2featmanip}. It uses the same approach as Sequential Forward Search, however it starts from a full set, and removes the "worst" feature at each stage.

Yu, L's paper \cite{subsetcover} recommends using set-cover to choose between forwards or backwards searches. The set cover provides a good hint at the final size of the feature set. 

A fourth subset search algorithm we covered is Sequential Floating Forward Selection SFFS\cite{PUDIL19941119}. In SFFS, the algorithm alternates between adding and removing features from the set. After every addition, it tests if it can improve performance by removing a feature. While performance improves, features continue being removed. When removal stops improving performance the algorithm will add another feature. This algorithm is not guaranteed to converge, so any implementations will need to keep track of already visited sets.

Embedded feature set selection/construction algorithms derive the feature subset during construction of the model.

CART DecisionTree\cite{breiman2017classification} can be used for both feature selection and feature construction. The feature list from the nodes of the tree is the feature subset. Additionally, the boolean equations in the nodes can be considered new boolean features, allowing rows to be mapped onto the path through the tree. This would simplify model use dramatically, converting tree walking into a value lookup.

A second embedded model is Support Vector Machines \cite{Cortes1995SupportvectorN}. The goal of the algorithm is to find the slope of a line between two classes that maximizes the distance between values in the class. Since it is mapping the input to a new set of dimensions, it is constructing features.

\subsection{Compare and contrast the performance of supervised filter, wrapper, and embedded methods}

Filter methods generalize best to different problems, are generally cheap and provide the worst accuracy.

Wrapper methods generalize the worst, are very expensive but provide the best accuracy.

Embedded methods are in the middle, providing accuracy, cost and generality between the other two.

Filter methods are cheap because they tend to be non-iterative. They are typically single pass with a final sort to obtain the final set. If they are performing complete subset searches, the evaluation function can be made incremental and does not involve training a model.

Wrapper methods are expensive because they will train an instance of the target model at least once per subset tested. If K-CV is used, multiple models will be trained for each subset.

Embedded methods have the same cost as Filter, and are cheaper than Wrapper methods. This is because once Filter selects a feature subset, it must train a model. An Embedded algorithm does this in a single pass producing the final model. Since Embedded only trains a single model, it will be cheaper than a Wrapper method which trains N models for each subset.

Filter methods do not evaluate the subsets in the final model, limiting their accuracy. However, the performance of the subset will be similar between models, allowing it to generalize better. Some filter methods do not evaluate subsets allow, only ranking features.

Wrapper methods, since they test against the specific algorithm and search through the available subsets are more likely to find subsets containing features that work well together, but have limited individual predictive power. This gives them high accuracy, but low generality. The feature subset is linked to the target model algorithm.

Embedded methods, like decision trees, make a single training pass. The algorithm performs feature selection during model construction. A wrapper around a decision tree will end up at the same tree while being more expensive.

\subsection{Correlation-based Feature Selection (CFS)1}

Yu, L. \cite{subsetcover} indicates that CFS is a Filter method. Reading Hall M.'s paper \cite{cfsHall}, CFS doesn't use a model, but does validate subsets instead of features individually. Since it doesn't use a model, it can't be embeded or wrapper, leaving filter the remaining class. CFS uses BestMatch, which is a complete search, so it will find the best subset match. Hall does recommend adding an early exit criteria to the algorithm. Any complete search will produce similar results. Single forward search was also tested.


\printbibliography

\end{document}