\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{references.bib}
\usepackage{amsmath}  % Basic math symbols and environments
\usepackage{amssymb}  % Extended symbol collection
\usepackage{mathtools} % Fixes and additions to amsmath
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{float}
\usepackage{csvsimple}
\usepackage[colorlinks=true]{hyperref}
\usepackage{indentfirst}
\newlength{\Lnote}
\newcommand{\note}[1]
{\addtolength{\leftmargini}{4em}
	\settowidth{\Lnote}{\textbf{Note:~}}
	\begin{quote}
		\rule{\dimexpr\textwidth-2\leftmargini}{1pt}\\
		\mbox{}\hspace{-\Lnote}\textbf{Note:~}%
		#1\\[-0.5ex] 
		\rule{\dimexpr\textwidth-2\leftmargini}{1pt}
	\end{quote}
	\addtolength{\leftmargini}{-4em}}
\begin{document}
\title{AIML427 - Big Data Assignment \#2}
author: Jason Pollock
email: jason@pollock.ca, pollocjaso@myvuw.ac.nz

\section{Manifold Learning}

\subsection{Question 1}
I picked \url{https://archive-beta.ics.uci.edu/dataset/579/myocardial+infarction+complications}{Myocardial infarction complications}. It has 111 features, and 1,700 instances. The purpose of the dataset is to predict complications that a patient will have at admission or the first 24, 48, or 72 hours after admission.

This matches the problem's requirements.

I spent hours searching through NZ Government public datasets, NOAA and other official sources of data. None of them support searching by "number of features". Eventually I found the University of California Irvine website. 

I have no interest in this dataset. I have no link to the underlying issues it is trying to help resolve. My interest is purely in attempting to meet the assignment's requirements.
\subsection{Question 2 - PCA}



\end{document}